Generative AI for image reconstruction\\ in Intensity Interferometry: a first attempt

### 2025-09-25 Phase_II/draft/response.txt

|  - There appears to be no correlation between the x and y centroids of the
|  star relative to the ground truth. This would be a serious problem? It
|  seems to do ok on the second moments, but no recovery at all of the third
|  moments. This may be related to section 5.3 which seems to lack any account
|  of gravity darkening, which is in the simulations.

Counter-argument: yes the centroids are showing noise -- all values
are around (63.5,63.5) which is the centre of the field -- but it is
not important, because absolute centroid is not a measurable quantity
in interferometry.

|  - No information is provided in the paper about computer systems. What
|  hardware was used (CPUs? GPUs?), and how long did it take for training and
|  for inference? It is important to quantify computational performance.

The information is provided and we use CPU for training. This work has used 2 nodes with 96 threads each,
which takes around 20 hours to train the model with 100000 training steps.

### 2025-09-25 Phase_II/draft/GAN.tex
before figure 7

Subsequently, zero padding is applied—adding rows and columns of zeros around the images—to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output. Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake. This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that the Generator uses as feedback.

>>>>

Subsequently, zero padding is applied, adding rows and columns of zeros around the images to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output. Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake. This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that the Generator uses as feedback.

### 2025-09-25 Phase_II/draft/ParaGan.tex
before figure 7

\section{Network Parameters}
\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{fig/testing_image/image_1.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_4.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_10.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_15.png}
\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work. Each row in this figure represents the results for a hypothetical fast-rotating star. Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (of Fig.\ref{fig:ft_base}). This image is presented, as the input, to the trained GAN to produce a predicted image. The second panel is the real image of the star, also called the ground truth. The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model . The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane. The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane. }
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II. Given the adversarial nature of GANs—where the Generator and Discriminator engage in a min-max game—careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.

>>>>

\section{Network Parameters}
\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{fig/testing_image/image_1.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_4.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_10.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_15.png}
\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work. Each row in this figure represents the results for a hypothetical fast-rotating star. Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (of Fig.\ref{fig:ft_base}). This image is presented, as the input, to the trained GAN to produce a predicted image. The second panel is the real image of the star, also called the ground truth. The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model . The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane. The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane. }
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II. Given the adversarial nature of GANs, where the Generator and Discriminator engage in a min-max game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.

### 2025-09-25 Phase_II/draft/Result.tex
before figure 7

\subsection{Predicted Image from the Trained GAN}
Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model to reconstruct the images of  fast-rotating stars using their Intensity Interferometry (II) observation . The GAN was trained on the training datasets for 60,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars. The training was performed on a CPU using two nodes, each with 96 threads, and required approximately nine hours. In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the stars' shape, size, and brightness distribution using II.
\begin{itemize}
\item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}
\item{The first middle panel displays the real image, or ground truth, which the Disciminator loss function uses to distinguish from the images generated by the Generator. During training, the GAN aims to keep minimum difference between these ground truth image and generated images.}
\item{The second middle panel presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
\item{The right panel shows the difference between the ground truth and the predicted image in the interferometric plane. The uniform background color of the frames suggests that the GAN model picks up white noise in the interferometric plane.}
\end{itemize}
The predicted images in Fig.~\ref{fig:GAN} yield encouraging results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines. However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming CTAO an ideal candidate for this approach.

>>>>

\subsection{Predicted Image from the Trained GAN}
Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model to reconstruct the images of  fast-rotating stars using their Intensity Interferometry (II) observation . The GAN was trained on the training datasets for 100,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars. The training was performed on a CPU using two nodes, each with 96 threads, and required approximately 20 hours. In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the stars' shape, size, and brightness distribution using II.
\begin{itemize}
\item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}
\item{The first middle panel displays the real image, or ground truth, which the Disciminator loss function uses to distinguish from the images generated by the Generator. During training, the GAN aims to keep minimum difference between these ground truth image and generated images.}
\item{The second middle panel presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
\item{The right panel shows the difference between the ground truth and the predicted image in the interferometric plane. The uniform background color of the frames suggests that the GAN model picks up white noise in the interferometric plane.}
\end{itemize}
The predicted images in Fig.~\ref{fig:GAN} yield encouraging results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines. However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming CTAO an ideal candidate for this approach.
